---
title: "3. Data preprocessing
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Processing database from previous step to arrive to a database which has each name for each article.

At the end, I arrive to two databases: one with only first names per authors of articles, and other that has last names as well. Analysis was done on the further step to explore whether the Python's gender APIs gains more information by using last name or not.

*To proceed with the gender identification, the initial data set (all_nograms_raw.RDS) is filtered so I stay with only those articles which have abstract.*

```{r}
library(jsonlite)
library(dplyr)
library(readtext)
library(stringr)
library(stringi)
```

*Load raw file*

```{r}
data_raw <- readRDS("/Users/carolinachru/Documents/LT/M498_Cap/data/jstor_constellate/final/all_nograms_raw.RDS")
head(data_raw)

sum(!is.na(data_raw$abstract)) # Num of non-NA abstracts

# Filter if it does not have an abstract
data_raw1 <- data_raw[is.na(data_raw$abstract) == FALSE,] 

sum(is.na(data_raw$id)) # Num of NA id
n_distinct(data_raw$id) == nrow(data_raw) # Duplicates? If true, then no duplicates

# Select dataframe only for authors
data_authors <- data_raw1 %>% select(id, starts_with("creator_"))
```
```{r}
# How many authors?
sum(!is.na(data_authors[,-c(1)]))
sum(is.na(data_authors[,-c(1)]))

```


### Extract first names

It seems we have the following cases in names:

(1) No first names: "R. J. Chelliah", "H. Öztaş Ayhan"
(2) One first name explicit, the other abbreviated: "Jennifer S. Haas", "RICHARD P. Barth", "M. Martin Boyer", "Paul G. J. O'Connell"
(3) One first name and one last name:  "Paul Hickman", "Kofi K. Nkrumah-Young"  
(4) Three names (indistinct whether one is first or last name): "Susan Tinsley Gooden", "Laura Parte Esteban", 
(5) Not names but institutions: "EPW Research Foundation", "South Centre"

As such, create one variable per "creator" (author) so that first this is identified. This helps creating a specific function to see how names are being extracted. Also, to identify those names which do not fall on any of those cases.

Paths: 
- If 2 words, extract the first.
- If +2 words, extract first 2.

Clean-up:
- If just one letter or letter with ".", omit.


```{r}
# Overview
sample(data_authors$creator_1, 100, replace = FALSE)
```

**Database for first name**

```{r}
# Test text for extraction
test0 <- c("R J. Chelliah", "H. Öztaş Ayhan", "Jennifer S. Haas", "M. Martin Boyer", "Paul G. J. O'Connell",
           "Kofi K. Nkrumah-Young", "Paul Hickman", "Susan Tinsley Gooden", "Laura Parte Esteban", "C. M Chavez",
           "Hans van Meijl", "Hans van Meijl", "Wynand P. M. M. van de Yen", "Jennifer Van Hook", "K.", "Carolina C.", "Carolina C", "Paul Hickman", "Paul G. J. O'Connell")


# Function for extraction of first name
extract_firstname <- function(astring){
  temp_length <- str_count(astring, " ") + 1
  first_name <- ifelse(temp_length <= 2, word(astring, start = 1), word(astring, start = 1, end = 2)) # Extract
  
  first_name <- gsub("[[:space:]]((VAN)|(van))\\>", " ", first_name)
  first_name <- gsub("[[:space:]]((DE)|(de))\\>", " ", first_name)
  first_name <- gsub("[[:space:]]((DER)|(der))\\>", " ", first_name)
  first_name <- gsub("[[:space:]]((VON)|(von))\\>", " ", first_name)
  first_name <- gsub("[[:space:]]((LA)|(la))\\>", " ", first_name)
  first_name <- gsub("[[:space:]]((DI)|(di))\\>", " ", first_name)
  first_name <- gsub("[[:space:]]((JR)|(Jr)|(Jr\\.)|(JR\\.))\\>", " ", first_name)  
  
  first_name <- gsub("\\<+[A-z](\\.)?[[:blank:]]", "", first_name) # Drop abbreviations like J. or G (beginning)
  first_name <- gsub("[[:space:]]*[A-Z](\\.)?$", "", first_name) # Drop abbreviations like J. or G (at the end)
  first_name <- trimws(first_name) # Remove leading or trailing blank space
  return(first_name)
}

# Application (to final data)
data_authors1 <- sapply(data_authors[, -c(1)], extract_firstname)
data_authors1 <- data.frame(data_authors[,1], data_authors1)

# Data cleaning
data_authors2 <- data_authors1
data_authors2[data_authors1 == ""] <- NA

# Save dataframe of names
write.csv(data_authors2, "/Users/carolinachru/Documents/LT/M498_Cap/data/jstor_constellate/final/all_authors_firstname.csv")
write.csv(data_authors, "/Users/carolinachru/Documents/LT/M498_Cap/data/jstor_constellate/final/all_authors_allname.csv")
```


### Extract author's order 

**Database for author's descriptive statistics**

Database contains:

- Number of authors in raw file
- Number of authors after last processing
- Alphabetically ordered or not
  - Case 1: using all last words
  - Case 2: if full name +3 words, then check 2nd from last
  
In case 2, the componentes "van" (e.g., van Berg) and "de" (e.g., de Alba) are removed if all letters are lower (van, de) or upper (VAN, DER). If the first letter is upper and following lower, then it is counted as a last name. This because in some sources, it said depending by country sometimes the components are taken as lastnames and other just as components. In this sense, I will 'respect' the reporting by authors.
  Source: https://academia.stackexchange.com/questions/8870/how-should-van-names-be-ordered-in-a-bibliography
  

```{r}
alphab_ordering <- function(df){
  
  obs <- nrow(df)
  final_df <- data.frame()
  
  # Row by row processing information
  for(i in 1:obs){
    temp_row <- as.character(df[i,-c(1)])
    
    # Number of authors
    not_na <- sum(!is.na(temp_row))
    
    # Clean names
    clean_names <- gsub("[[:space:]]((VAN)|(van))[[:space:]]", " ", temp_row)
    clean_names <- gsub("[[:space:]]((DE)|(de))[[:space:]]", " ", clean_names)
    clean_names <- gsub("[[:space:]]((DER)|(der))[[:space:]]", " ", clean_names)
    clean_names <- gsub("[[:space:]]((VON)|(von))[[:space:]]", " ", clean_names)
    clean_names <- gsub("[[:space:]]((LA)|(la))[[:space:]]", " ", clean_names)
    clean_names <- gsub("[[:space:]]((DI)|(di))[[:space:]]", " ", clean_names)
    clean_names <- gsub("[[:space:]]((JR)|(Jr)|(Jr\\.)|(JR\\.))\\>", " ", clean_names)
    
    clean_names <- gsub("\\<+[A-z](\\.)?[[:blank:]]", "", clean_names) # Names without the A. or A
    clean_names <- str_replace_all(clean_names, "  ", " ") # Remove double spaces

    # Letter from last name
    lastname <- word(clean_names, start = -1)
    
    # Alphabetical - CASE 1
    alphab_case1 <- ifelse(not_na == 1, NA, 
                           ifelse(identical(lastname[1:not_na], sort(lastname)), TRUE, FALSE))
    
    # Alphabetical - CASE 2
    name_len <- sapply(strsplit(clean_names[1:not_na], " "), length) # Length
    lastname_case2 <- ifelse(name_len > 2, 
                                    word(clean_names[1:not_na], start = -2),
                                    word(clean_names[1:not_na], start = -1))
    alphab_case2 <- ifelse(not_na == 1, NA, 
                           ifelse(identical(lastname_case2, sort(lastname_case2)), TRUE, FALSE))
    
    # Last names used
    names(lastname) <- paste0("lastname_c1_", 1:62)
    names(clean_names) <- paste0("lastname_c2_", 1:62)
    last_names_cases <- data.frame(as.list(c(lastname, clean_names)))
    
    # All original names
    names(temp_row) <- paste0("allname_", 1:62) 
    temp_row_df <- data.frame(as.list(temp_row))
    
    # Final database
    temp_df0 <- data.frame(id = df[i,1],
                          num_authors = not_na,
                          alpha_case1 = alphab_case1,
                          alpha_case2 = alphab_case2)
    temp_df <- bind_cols(temp_df0, temp_row_df) # Initial names
    final_df <- bind_rows(final_df, temp_df)
  }
  
  return(final_df)
}

#data_authors100_alpha <- alphab_ordering(data_authors100)
data_authors_alphab <- alphab_ordering(data_authors)

# Final data
write.csv(data_authors_alphab, "/Users/carolinachru/Documents/LT/M498_Cap/data/jstor_constellate/final/all_authors_alphab.csv")

```

### Command testing

```{r}
data_authors100 <- data_authors[1:100,]
y <- as.character(data_authors100[7,-c(1)])

# Number of authors 
not_na <- sum(!is.na(y))

# Clean last name
clean_names <- gsub("[[:space:]]((VAN)|(van))[[:space:]]", " ", y)
clean_names <- gsub("[[:space:]]((DE)|(de))[[:space:]]", " ", clean_names)
clean_names <- gsub("\\<+[A-z](\\.)?[[:blank:]]", "", clean_names) # Names without the A. or A
clean_names <- str_replace_all(clean_names, "  ", " ") # Remove double spaces

# Letter from last name
lastname <- word(clean_names, start = -1)

# Alphabetical - CASE 1
alphab_case1 <- ifelse(not_na == 1, NA, 
                       ifelse(identical(lastname[1:not_na], sort(lastname)), TRUE, FALSE))

# Alphabetical - CASE 2
name_len <- sapply(strsplit(clean_names[1:not_na], " "), length) # Length
lastname_case2 <- ifelse(name_len > 2, 
                                word(clean_names[1:not_na], start = -2), #aquii
                                word(clean_names[1:not_na], start = -1))
alphab_case2 <- ifelse(not_na == 1, NA, 
                       ifelse(identical(lastname_case2, sort(lastname_case2)), TRUE, FALSE))



```

```{r commands-test}
# Identify total world length
str_count(test0, " ") + 1

# Identify first and second words
word(test0, start = 1, end = 2)

# Identify J. or J abbreviations
str_extract(test0,"[A-z]*[.]")

# Identify last word
word(test0, start = -1)

# Identify letter from last name
str_extract(word(test0, start = -1), "^[A-Z]")

# About "van" and "de"
test1 <- c("ARMIN VAN BURREN Delta DELTA", "Hans van Meijl", "Hans van Meijl", 
           "Evan YAN", "Jennifer Van Hook Vandel", 
           "Ola de Alba", "OLA DE MUHOC", "Hola De Joy")
test2 <- c("Kelvin Choi", "Deborah J Hennrikus", "Jean L Forster", "Molly Moilanen")

# Extract de or DE, or van or VAN
str_extract(test1, "[[:space:]]((VAN)|(van))[[:space:]]")
```



