---
title: "5. Gender preprocessing
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Processing databases that have already identified the gender for authors.

```{r}
library(jsonlite)
library(dplyr)
library(readtext)
library(stringr)
library(stringi)
library(tidyr)
library(cld3)
library(cld2)
library(textcat)
```

```{r}
# Read
df_both0 <- read.csv("/Users/carolinachru/Documents/LT/M498_Cap/data/jstor_constellate/final/gender_3cases/final_gender_both.csv")
df_gen0 <- read.csv("/Users/carolinachru/Documents/LT/M498_Cap/data/jstor_constellate/final/gender_3cases/final_gender_Pgender.csv")
df_gC0 <- read.csv("/Users/carolinachru/Documents/LT/M498_Cap/data/jstor_constellate/final/gender_3cases/final_gender_PgenderC.csv")

```

Merge with the rest of the information

```{r}
data_raw <- readRDS("/Users/carolinachru/Documents/LT/M498_Cap/data/jstor_constellate/final/all_nograms_raw.RDS")
sum(!is.na(data_raw$abstract)) # Num of non-NA abstracts
data_raw1 <- data_raw[is.na(data_raw$abstract) == FALSE,] # Filter if it does not have an abstract

df_both <- df_both0 %>% left_join(data_raw1, by = "id") %>% select(-paste0("creator_", 1:62))
df_gen <- df_gen0 %>% left_join(data_raw1, by = "id") %>% select(-paste0("creator_", 1:62))
df_gC <- df_gen0 %>% left_join(data_raw1, by = "id") %>% select(-paste0("creator_", 1:62))

```

Detect language
```{r}
# Package cld2 ("en")
df_both$language_both <- cld2::detect_language(df_both$abstract)
df_gen$language_gen <- cld2::detect_language(df_gen$abstract)
df_gC$language_gC <- cld2::detect_language(df_gC$abstract)

# Package cld3 ("en")
df_both$language_both2 <- cld3::detect_language(df_both$abstract)
df_gen$language_gen2 <- cld3::detect_language(df_gen$abstract)
df_gC$language_gC2 <- cld3::detect_language(df_gC$abstract)
```

- With textcat, journals

```{r}
# Remove non-english abstracts
df_both1 <- df_both %>% filter(language_both == "en" & language_both2 == "en") 
df_gen1 <- df_gen %>% filter(language_gen == "en" & language_gen2 == "en")
df_gC1 <- df_gC %>% filter(language_gC == "en" & language_gC2 == "en")
```

cld2 is better for journals. 2 problems: if mix language (example, "Amerikastudien / American Studies"), then it says english -> solution: drop journals with "/". also, there are others which are NA that are important such as "Econometrica". solution: this manually.

```{r}
# Remove non-english journals, function
clean_journals <- function(df){
  journals <- data.frame(table(df$isPartOf))
  journals$title <- as.character(journals$Var1)
  journals$lang3 <- cld3::detect_language(journals$title)
  journals$lang2 <- cld2::detect_language(journals$title)
  journals$joint <- str_detect(journals$title, "\\/")
  
  # Keep if english or NA, drop if it has "/"
  journals_fin <- journals %>% filter(joint == FALSE & (lang2 == "en" | is.na(lang2))) %>% select(-joint)
  
  return(journals_fin)
}

journals_both0 <- clean_journals(df_both1)
journals_gC0 <- clean_journals(df_gC1)
journals_gen0 <- clean_journals(df_gen1)
```


```{r}
# Manually check for NA language, all three datasets
all_na_journals <- c(journals_both0$title[is.na(journals_both0$lang2)],
                  journals_gC0$title[is.na(journals_gC0$lang2)],
                  journals_gen0$title[is.na(journals_gen0$lang2)])
all_na_journals <- names(table(all_na_journals))
```

Using `all_na_journals` object, an Excel file is created for classification. The results are the following:

```{r}
# Upload the manually classificated articles
na_journals <- read.csv("/Users/carolinachru/Documents/LT/M498_Cap/data/jstor_constellate/journals_manual.csv")
```

Remove journals not in english
```{r}
# Journals with NA (cld2) to keep
na_journals_keep <- na_journals %>% filter(english == "Yes")
na_journals_keep <- na_journals_keep$name

# Journals in english (cld2) to keep
all_eng_journals <- c(journals_both0$title[journals_both0$lang2 == "en"],
                      journals_gC0$title[journals_gC0$lang2 == "en"],
                      journals_gen0$title[journals_gen0$lang2 == "en"])
eng_journals_keep <- names(table(all_eng_journals))

fin_journals_keep <- c(na_journals_keep, eng_journals_keep)

# Both
journal_clean <- function(df){
  df_final <- df %>% mutate(isPartOf_eng = ifelse(isPartOf %in% fin_journals_keep, TRUE, FALSE)) %>% 
    filter(isPartOf_eng == TRUE) %>% rename(journal = isPartOf) %>% select(-isPartOf_eng)
  return(df_final)
}
df_both2 <- journal_clean(df_both1)
df_gC2 <- journal_clean(df_gC1)
df_gen2 <- journal_clean(df_gen1)

```

Cleaning by tdmCategory and sourceCategory

What is the difference? 
- tdmCategory:	the inferred category of the content based on machine learning
- sourceCategory:	the category according to the provider

```{r}
# Same categories for each 3 datasets (both, gen and gC)
tdm0 <- df_both1 %>% select(starts_with("tdmC"))
source0 <- df_both1 %>% select(starts_with("sourceC"))
tdm_vec <- as.vector(as.matrix(tdm0))
source_vec <- as.vector(as.matrix(source0))

tdm_unique <- names(table(tdm_vec))
source_unique <- data.frame(table(source_vec))
```

```{r}
# Upload the manually classificated articles
source_ca <- read.csv("/Users/carolinachru/Documents/LT/M498_Cap/data/jstor_constellate/sourcecategory_manual.csv")
```

Control for economics literature.

- if all sourceCategory_* not relevant, drop.
- if sourceCat NA, but tdm econ/politics/social ok.
- if at least one sourceCategory_* not relevant, but tdm econ/politics/social ok

```{r}
# Finally selected categories
source_ca <- source_ca$source_cat[source_ca$social_sci == TRUE]
source_ca <- iconv(source_ca, from = 'UTF-8', to = 'ASCII//TRANSLIT')

# Function for selecting non-relevant categories
category_clean <- function(df0, vec){
  df <- df0
  vars_source <- df %>% select(starts_with("sourceC")) 
  df_source <- sapply(vars_source, 
                  function(x){ifelse(is.na(x), NA, ifelse(x %in% vec, TRUE, FALSE))}) # If it is, TRUE
  df$source_rel <- rowSums(df_source, na.rm = TRUE)
  df$source_tot <- rowSums(!is.na(df_source))
  df$source_tot_na <- ifelse(rowSums(is.na(df_source)) == 10, TRUE, FALSE)
  df$tdm_econ <- str_detect(df$tdmCategory_1, "(Economics)|(Political)|(Social)")
  df$tdm_econ2 <- str_detect(df$tdmCategory_2, "(Economics)|(Political)|(Social)")
  df <- df %>% mutate(unrel = case_when(source_rel == 0 & source_tot_na == FALSE ~ "drop",
                                       (source_rel < source_tot) & source_tot_na == FALSE & 
                                         tdm_econ == FALSE & tdm_econ2 == FALSE ~ "drop",
                                       source_tot == TRUE & tdm_econ == FALSE & tdm_econ2 == FALSE ~ "drop"))
  return(df)
}
df_both3 <- category_clean(df_both2, source_ca)
df_gen3 <- category_clean(df_gen2, source_ca)
df_gC3 <- category_clean(df_gC2, source_ca)


```

Several articles which start the abstract variable with "ABSTRACT", "Abstract", "ABSTRACT."

```{r}
# Function to clean abstract
# Remove the word "abstract" from abstracts
abstract_clean <- function(df0){
  df <- df0
  
  # Identify all forms that the word "abstract" exists
  abstracts <- df %>% 
    mutate(starts = str_extract(abstract, "^((Abstract)|(ABSTRACT)|(abstract))[[:punct:]]*")) %>%
    select(starts)
  abstracts_pres <- names(table(abstracts))

  # Substitute each case
  for(i in 1:length(abstracts_pres)){
    df$abstract <- sub(abstracts_pres[i], "", df$abstract, fixed = TRUE)
  }
  # Clean punctuation left or leading white space 
  df$abstract <- sub("^[[:punct:]]?", "", df$abstract)
  df$abstract <- trimws(df$abstrac, which = "left")
  
  return(df)
}

df_both4 <- abstract_clean(df_both3)
df_gen4 <- abstract_clean(df_gen3)
df_gC4 <- abstract_clean(df_gC3)

```

Save

```{r}
write.csv(df_both4, "/Users/carolinachru/Documents/LT/M498_Cap/data/jstor_constellate/final/final_bothP.csv")
write.csv(df_gen4, "/Users/carolinachru/Documents/LT/M498_Cap/data/jstor_constellate/final/final_Pgender.csv")
write.csv(df_gC4, "/Users/carolinachru/Documents/LT/M498_Cap/data/jstor_constellate/final/final_PgenderC.csv")
```

```{r command_test}
# Remove non-english journals
journals_both <- data.frame(table(df_both1$isPartOf))
journals_both$title <- as.character(journals_both$Var1)
journals_both$lang3 <- cld3::detect_language(journals_both$title)
journals_both$lang2 <- cld2::detect_language(journals_both$title)
journals_both$joint <- str_detect(journals_both$title, "\\/")
journals_both_fin <- journals_both %>% filter(joint == FALSE & (lang2 == "en" | is.na(lang2)))

# Evaluate sourceCat
df_both2_B <- df_both2
vars_source <- df_both2_B %>% select(starts_with("sourceC"))
test0 <- sapply(vars_source, 
                function(x){ifelse(is.na(x), NA, ifelse(x %in% source_ca, TRUE, FALSE))}) # TRUE, si esta
df_both2_B$source_rel <- rowSums(test0, na.rm = TRUE)
df_both2_B$source_tot <- rowSums(!is.na(test0))
df_both2_B$tdm_econ <- str_detect(df_both2_B$tdmCategory_1, "(Economics)|(Political)|(Social)")
df_both2_2 <- df_both2_B %>% mutate(unrel = case_when(source_rel == 0 ~ "drop",
                                        (source_rel < source_tot) & tdm_econ == FALSE ~ "drop"))

# Clean abstract
abstracts <- df_both3 %>% mutate(starts = str_extract(abstract, "^((Abstract)|(ABSTRACT)|(abstract))[[:punct:]]*")) %>% select(starts)
abstracts_pres <- names(table(abstracts))

test0 <- df_both3[!(is.na(abstracts)), c("id", "abstract")]
# Substitute each case
for(i in 1:length(abstracts_pres)){
  test0$abstract <- sub(abstracts_pres[i], "", test0$abstract, fixed = TRUE)
}
# Clean punctuation left or leading white space 
test0$abstract <- sub("^[[:punct:]]?", "", test0$abstract)
test0$abstract <- trimws(test0$abstrac, which = "left")


  
test0 <- df_both3[!(is.na(abstracts)), c("id", "abstract")]
```
